\prefacesection{Acknowledgements}
As I was writing these lines of acknowledgements, it struck me that 5 years have
already passed, blazingly fast but truly rewarding. At the beginning of my PhD,
I thought it would be a long, painful multi-year period of my life (yes, there
had been ups and downs!), but by the time I was close to finishing, my PhD
duration became surprising short as I kept wandering: will I ever have a chance
to live again in such a stimulating, inspiring, and caring environment with
little pressure and full freedom for academic and personal development that
Stanford and the CS department had offered? All of my achievements will not be
possible without the help of many people.

First and foremost, I would like to extend my deepest appreciation to my
advisor, Chris Manning, whom I cannot find any point to complain about. Chris
has given me so much inspiration for my academic career and provided me
countless support including personal matters. Without him, it will be uncertain
if I can make it all the way through my PhD. To get a sense of Chris's hard work,
I invite readers to visit this link
\url{https://github.com/lmthang/thesis/issues} which documents all of his edits
to my thesis, page by page.

I would also like to thank other members in my thesis committee, Dan Jurafsky,
Andrew Ng, Quoc Le, and Christopher Potts for providing feedback to my thesis
and making sure I can graduate. I am grateful to Quoc Le, Ilya Sutskever,
Oriol Vinyals, and other colleagues at Google Brain who have inspired me to do
research in deep learning. It was a fortunate turn of my life when interning at
Google Brain in 2014 and 2015 during which I had learned how to train my first
deep neural network in Neural Machine Translation! Quoc Le deserves special
mention for being my main hosts during these two internships and for having
enlightened me with his vision on AI.


I am thankful to my other collaborators (in chronological order) whom I have
learned so much from: Michael C. Frank, Mark Johnson, Richard Socher, Wojciech
Zaremba, Hieu Pham, Michael Kayser, Jiwei Li, Eudard Hovy, Lukasz Kaiser, Tim
O'Donnell, Noah Goodman, Kyunghuyn Cho, Joern Wuebker, Spence Green, John
DeNero, Sa\v{s}a Hasan, and Abigail See. I would like to thank members of the
Stanford NLP group which I am fortunate to be in; 5 years are simply too short
to learn from all of you and I will definitely miss the many retreats, BBQs,
paper review sessions, NLP lunch seminars, conference trips, etc., that we had
together. I would like to thank friends in the CS department whom I always look
up to and strive to be ``equally good''. I would like to specifically thank Percy
Liang for being in my qualifying exam committee and Russell Stewart for always
enlightening me with his intelligence. I would like to thank staff in the Gates
building who have been silently providing support for generations of successful
students.

Certainly, life is meaningless without close friends and family. I would like to
thank all people whom I have been with me, encouraging me, and providing me with
unwavering support to finally complete this journey. These include Wendy Nguyen,
Luan Nguyen, Edward Pham, Hanh Pham, Ca Truong, Hoan Nguyen, An Nguyen, Ngoc Do,
Vu Van, Vy Van, Huong Ha, Cindy Au, Minh Thao Nguyen, Lan Huong Nguyen, Trang
Nguyen, Huy Le, Thai Pham, Hai Vo, Thuc Vu, friends in the VietStan family, and
many many others which I am grateful for.

Last but not least, I would like to
thanks my parents, Binh Luong and Thuy Nguyen, as well as my dear brother, Toan
Luong. They have been and will always be my strongest support!
